MS-4.2 Types of Relationships

### 2021-01-20 ms-a1_formulae-and-equations.rmd
Changed icons and theme.

# [Syllabus](https://syllabus.nesa.nsw.edu.au/assets/mathematics_standard/mathematics-standard-stage-6-syllabus-2017.pdf) {.tabset .tabset-fade .tabset-pills}

@@

* review substitution of numerical values into linear and non-linear algebraic expressions and equations
  + review evaluating the subject of a formula, given the value of other pronumerals in the formula
  + change the subject of a formula
  + solve problems involving formulae, including calculating distance, speed and time (with change of units of measurement as required) or calculating stopping distances of vehicles using a suitable formula
* develop and solve linear equations, including those derived from substituting values into a formula, or those developed from a word description
* calculate and interpret blood alcohol content (BAC) based on drink consumption and body weight
  + use formulae, both in word form and algebraic form, to calculate an estimate for blood alcohol content $(BAC)$, including $BAC_{Male}=\frac{10N-7.5H}{6.8M}$ and $BAC_{Female}=\frac{10N-7.5H}{5.5M}$ where $N$ is the number of standard drinks consumed, $H$ is the number of hours of drinking, and $M$ is the person's weight in kilograms.
  + determine the number of hours required for a person to stop consuming alcohol in order to reach zero BAC, eg using the formula $time=\frac{BAC}{0.015}$
  + describe the limitations of methods estimating BAC
* calculate required medication dosages for children and adults from packets, given age or weight, using Fried’s, Young’s or Clark’s formula as appropriate
  + Fried's formula: Dosage for children 1-2 years $=\frac{\text{age (in months)}\ \times\ \text{adult dosage}}{150}$
  + Young's formula: Dosage for children 1-12 years $=\frac{\text{age of child (in years)}\ \times\ \text{adult dosage}}{\text{age od child (in years)}\ +\ 150}$
  + Clark's formula: Dosage $=\frac{\text{weight in kg}\ \times\ \text{adult dosage}}{70}$
:::

# Substitution [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A1/a_substitution.pdf){target="blank"} {.tabset .tabset-fade .tabset-pills}

>>>>

# Syllabus [![](open.svg){width=16}](https://syllabus.nesa.nsw.edu.au/assets/mathematics_standard/mathematics-standard-stage-6-syllabus-2017.pdf){target="blank"} {.tabset .tabset-fade .tabset-pills}

@@

* review substitution of numerical values into linear and non-linear algebraic expressions and equations
  + review evaluating the subject of a formula, given the value of other pronumerals in the formula
  + change the subject of a formula
  + solve problems involving formulae, including calculating distance, speed and time (with change of units of measurement as required) or calculating stopping distances of vehicles using a suitable formula
* develop and solve linear equations, including those derived from substituting values into a formula, or those developed from a word description
* calculate and interpret blood alcohol content (BAC) based on drink consumption and body weight
  + use formulae, both in word form and algebraic form, to calculate an estimate for blood alcohol content $(BAC)$, including $BAC_{Male}=\frac{10N-7.5H}{6.8M}$ and $BAC_{Female}=\frac{10N-7.5H}{5.5M}$ where $N$ is the number of standard drinks consumed, $H$ is the number of hours of drinking, and $M$ is the person's weight in kilograms.
  + determine the number of hours required for a person to stop consuming alcohol in order to reach zero BAC, eg using the formula $time=\frac{BAC}{0.015}$
  + describe the limitations of methods estimating BAC
* calculate required medication dosages for children and adults from packets, given age or weight, using Fried’s, Young’s or Clark’s formula as appropriate
  + Fried's formula: Dosage for children 1-2 years $=\frac{\text{age (in months)}\ \times\ \text{adult dosage}}{150}$
  + Young's formula: Dosage for children 1-12 years $=\frac{\text{age of child (in years)}\ \times\ \text{adult dosage}}{\text{age od child (in years)}\ +\ 150}$
  + Clark's formula: Dosage $=\frac{\text{weight in kg}\ \times\ \text{adult dosage}}{70}$

<div align="right"><i><small>As of 2021/01/20</small></i></div>
:::

# Substitution [![](pres.svg){width=16}](https://claytonpollard.github.io/stage6_standard_presentations/MS-A1/a_substitution.pdf){target="blank"} {.tabset .tabset-fade .tabset-pills}

### 2021-01-20 ms-a4-2_non-linear-relationships.rmd
Changed icons and theme.

# Exponential Functions [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2/a_exponential-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}

@@

# Exponential Models [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2/b_exponential-models.html){target="blank"} {.tabset .tabset-fade .tabset-pills}

@@

# Quadratic Functions [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2/c_quadratic-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}

>>>>

# Exponential Functions [![](pres.svg){width=16}](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2/a_exponential-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}

@@

# Exponential Models [![](pres.svg){width=16}](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2/b_exponential-models.html){target="blank"} {.tabset .tabset-fade .tabset-pills}

@@

# Quadratic Functions [![](pres.svg){width=16}](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2/c_quadratic-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
